Fast approximate Bayesian inference of HIV indicators using PCA adaptive Gauss-Hermite quadrature

### 2024-12-29 src/docs_paper-jtb/preamble.tex
Add JTB template
Use bookdown::pdf_book and complete first plausible version

\RequirePackage{amsthm,amsmath,amsfonts,amssymb}
\RequirePackage{bm}
\RequirePackage{enumerate}
\RequirePackage{enumitem}
\RequirePackage{tabularx}
\RequirePackage{adjustbox}
\RequirePackage{tikz}
\RequirePackage{bbm}
\RequirePackage{lscape}
\RequirePackage{booktabs}
\RequirePackage{longtable}
\RequirePackage{lscape}
\RequirePackage{pifont}
\usepackage{footnote}
\usepackage{algorithm}
\usepackage{algpseudocode}

\newcommand{\Sc}{\mathcal{S}}
\newcommand{\R}{\mathcal{R}}
\newcommand{\N}{\mathcal{N}}
\newcommand{\X}{\mathcal{X}}
\newcommand{\m}{\mathbf{m}}
\newcommand{\bu}{\mathbf{u}}
\newcommand{\bv}{\mathbf{v}}
\newcommand{\w}{\mathbf{w}}
\newcommand{\x}{\mathbf{x}}
\newcommand{\y}{\mathbf{y}}
\newcommand{\z}{\mathbf{z}}
\newcommand{\bb}{\mathbf{b}}
\newcommand{\bphi}{\bm{\phi}}
\newcommand{\bpsi}{\bm{\psi}}
\newcommand{\brho}{\bm{\rho}}
\newcommand{\btheta}{\bm{\theta}}
\newcommand{\bmeta}{\bm{\eta}}
\newcommand{\bmu}{\bm{\mu}}

@@

\definecolor{lightblue}{HTML}{56B4E9}
\definecolor{lightgreen}{HTML}{009E73}
\definecolor{lightorange}{HTML}{E69F00}
\definecolor{lightgrey}{HTML}{E6E6E6}

\newcommand{\lightblueline}{\raisebox{2pt}{\tikz{\draw[-,lightblue,solid,line width = 3pt](0,0) -- (2mm,0);}}}
\newcommand{\lightgreenline}{\raisebox{2pt}{\tikz{\draw[-,lightgreen,solid,line width = 3pt](0,0) -- (2mm,0);}}}
\newcommand{\lightorangeline}{\raisebox{2pt}{\tikz{\draw[-,lightorange,solid,line width = 3pt](0,0) -- (2mm,0);}}}
\newcommand{\lightgreyline}{\raisebox{2pt}{\tikz{\draw[-,lightgrey,solid,line width = 3pt](0,0) -- (2mm,0);}}}

>>>>

\RequirePackage{amsthm,amsmath,amsfonts,amssymb}
\RequirePackage{bm}
% \RequirePackage{enumerate}
% \RequirePackage{enumitem}
\RequirePackage{tabularx}
% \RequirePackage{adjustbox}
% \RequirePackage{tikz}
% \RequirePackage{bbm}
% \RequirePackage{lscape}
% \RequirePackage{booktabs}
% \RequirePackage{longtable}
% \RequirePackage{lscape}
% \RequirePackage{pifont}
% \usepackage{footnote}
% \usepackage{algorithm}
% \usepackage{algpseudocode}

\newcommand{\Sc}{\mathcal{S}}
\newcommand{\R}{\mathcal{R}}
\newcommand{\N}{\mathcal{N}}
\newcommand{\X}{\mathcal{X}}
\newcommand{\m}{\mathbf{m}}
\newcommand{\bk}{\mathbf{k}}
\newcommand{\bu}{\mathbf{u}}
\newcommand{\bv}{\mathbf{v}}
\newcommand{\w}{\mathbf{w}}
\newcommand{\x}{\mathbf{x}}
\newcommand{\y}{\mathbf{y}}
\newcommand{\z}{\mathbf{z}}
\newcommand{\bb}{\mathbf{b}}
\newcommand{\Hb}{\mathbf{H}}
\newcommand{\bphi}{\bm{\phi}}
\newcommand{\bpsi}{\bm{\psi}}
\newcommand{\brho}{\bm{\rho}}
\newcommand{\btheta}{\bm{\theta}}
\newcommand{\bmeta}{\bm{\eta}}
\newcommand{\bmu}{\bm{\mu}}

@@
